Reproducibility in plant pathology: where do we stand and a way forward

### 2021-06-21 analysis/paper/paper.Rmd
Update paper.Rmd

For us to easily discuss the topic, we first must define what we mean so that we may clearly communicate.
Many of the terms used in this area have varying definitions that may or may not agree with each other.
For instance, reproducible research is recently highlighted by many authors [@preeyanon2018; @Wallach2018; @Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.

@@

In biological sciences it is not always possible to use identical test material or perhaps the the time or resources are not available for full reproduction, _e.g._, field trials that span years and locations or complex glasshouse experiments.
Therefore, we will follow Peng's [-@Peng2009] definition that provides clear guidelines a minimum standard of "reproducible research":

@@

>>>>

For us to easily discuss the topic, we first must define what we mean so that we may clearly communicate.
Many of the terms used in this area have varying definitions that may or may not agree with each other.
For instance, reproducible research was recently highlighted by many authors [@preeyanon2018; @Wallach2018; @Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.

@@

In the biological sciences it is not always possible to use identical test material or perhaps the the time or resources are not available for full reproducibility, _e.g._, field trials that span years and locations or complex glasshouse experiments.
Therefore, we will follow Peng's [-@Peng2009] definition that provides clear guidelines for a minimum standard of "reproducible research":

@@

It goes without saying that plant pathologists already provide information on protocols and chemicals allowing for reproducibility. However, very often biological specimens such as strains, cultures or cultivars are often not available. These cases of a lack of reproducibility will not be covered here.
